Implementation of an Open-Source modular mangetic field camera hardware for usage in Low-Field MRI Systems

### 2023-10-15 documentation/paper/main.tex
.

The collection and subsequent processing of the data read from the sensor array is carried out on another computer system (host).
For this purpose, the Python framework is used, which was specially developed for the automated processing of magnetic field sensor data.
By adapting the sensor software on the basis of the documentation, a direct evaluation of the sensor is possible through the library.
Through the implemented auto-numbering routine and the feedback of this to the host software, each individual sensor is assigned to an individual measurement in the host software.

>>>>

The collection and subsequent processing of the data read from the sensor array is carried out on another computer system (host).
For this purpose, the Python framework is used, which was specially developed for the automated processing of magnetic field sensor data.
By adapting the sensor software on the basis of the documentation, a direct evaluation of the sensor is possible through the library.
Through the implemented auto-numbering routine and the feedback of this to the host software, each individual sensor is assigned to an individual measurement file in the host software.
